---
title: "Untitled"
author: "Luke Daniels"
date: "1/30/2018"
output: 
  beamer_presentation: 
    fonttheme: professionalfonts
    incremental: yes
    theme: Dresden
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Slide Title 

This is still the markdown text, for display on the screen but these are **slides** so we don't want to add too much text!

## Second Slide 

  - First incremental bullet point
  - Second incremental bullet point
  - Thid incremental bullet point 
  
## Third Slide 
>- first simultaneous bullet point 
>- second simultaneous bullet point
>- third simultaneous bullet point 

## Let's see some R 

```{r, echo=FALSE}
library(ggplot2)
var1 <- runif(10)
var2 <- runif(10)
qplot(x=var1, y=var2) 
```

## Colored Bullet Points 
>- Collection Mode
>- \color{gray} Spatial and Temporal 
>- \color{red} Taxonomic Bias 
>- \color{gray} Sampling \color{black}
>- more stuff 

## Pulling in images

 \begin{picture}(320,250)
 \put(85,75){\includegraphics[height=6cm]
 {celtic.jpg}}
 \put(00,60){\begin{minipage}[t]{1\linewidth}
 {Choose a point on the unit circle. Connect it to the origin with a line of length one, and denote the angle between that line and the horizontal 
 coordinate axis by $\theta$.}
 \end{minipage}}
 \end{picture}

